Effects of CHILDREN's programs

### 2020-02-27 paper.tex
adapted paper

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 20:41:58 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccccc}
  \hline
 & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
1 & 2011 & 3748.0 &  & 52 &  \\ 
  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

\begin{table}
\caption{Association between selfworth and subsidy per beneficiary}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & (1) & (2) & (3) & (4) \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
Num. obs.                      & 428      & 184      & 430      & 187      \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
\hline
\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{SelfworthRegressions}
\end{center}
\end{table}

\begin{table}
\caption{Association between everyday expertise and subsidy per beneficiary}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & (1) & (2) & (3) & (4) \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
                               & $(0.00)$ &          & $(0.00)$ &          \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
                               &          & $(0.00)$ &          & $(0.00)$ \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
Num. obs.                      & 426      & 177      & 429      & 181      \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
\hline
\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{DayToDaySkillsRegressions}
\end{center}
\end{table}

@@

\begin{table}
\caption{Association between healthy meals criterion and beneficiaries being less ill}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & (1) & (2) & (3) & (4) \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
Num. obs.           & 121          & 120         & 177          & 177          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
\hline
\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{HealthRegressions-LessIll}
\end{center}
\end{table}

\begin{table}
\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & (1) & (2) & (3) & (4) \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
Num. obs.           & 214      & 212      & 275        & 275      \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
\hline
\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{HealthRegressions-DietaryKnowledge}
\end{center}
\end{table}

\begin{table}
\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c }
\hline
 & (1) & (2) & (3) & (4) \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
Num. obs.           & 213          & 211      & 274          & 274        \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
\hline
\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{HealthRegressions-AppreciateHealthy}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 8:42:23 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
  \label{lessIllOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 8:42:24 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
  \label{dietaryOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 8:42:24 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
  \label{appreciateOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Feb 27 22:26:53 2020
\begin{table}[ht]
\centering
\begin{tabular}{lccccc}
  \hline
 & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
1 & 2011 & 3748.0 &  & 52 &  \\ 
  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{fundamentalDynamics}
\end{table}

@@

\begin{table}
\caption{Association between selfworth and subsidy per beneficiary}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c c }
\hline
 & (1) & (2) & (3) & (4) & (5) \\
\hline
(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
                               &          & $(0.00)$ &          & $(0.00)$ &              \\
ML1                            &          &          &          &          & $0.24^{***}$ \\
                               &          &          &          &          & $(0.06)$     \\
ML2                            &          &          &          &          & $0.37^{***}$ \\
                               &          &          &          &          & $(0.05)$     \\
ML3                            &          &          &          &          & $0.15^{***}$ \\
                               &          &          &          &          & $(0.04)$     \\
\hline
R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
\hline
\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{SelfworthRegressions}
\end{center}
\end{table}

\begin{table}
\caption{Association between everyday expertise and subsidy per beneficiary}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c c c }
\hline
 & (1) & (2) & (3) & (4) & (5) & (6) \\
\hline
(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
ML4                            &          &          &          &          &              & $0.49^{***}$ \\
                               &          &          &          &          &              & $(0.06)$     \\
\hline
R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
\hline
\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{DayToDaySkillsRegressions}
\end{center}
\end{table}

@@

\begin{table}
\caption{Association between healthy meals criterion and beneficiaries being less ill}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c c }
\hline
 & (1) & (2) & (3) & (4) & (5) \\
\hline
(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
ML1                 &              &             &              &              & $0.12^{*}$   \\
                    &              &             &              &              & $(0.06)$     \\
ML2                 &              &             &              &              & $0.27^{***}$ \\
                    &              &             &              &              & $(0.06)$     \\
\hline
R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
\hline
\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{HealthRegressions-LessIll}
\end{center}
\end{table}

\begin{table}
\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c c }
\hline
 & (1) & (2) & (3) & (4) & (5) \\
\hline
(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
ML1                 &          &          &            &          & $0.26^{***}$ \\
                    &          &          &            &          & $(0.06)$     \\
ML2                 &          &          &            &          & $0.24^{***}$ \\
                    &          &          &            &          & $(0.06)$     \\
ML3                 &          &          &            &          & $0.37^{***}$ \\
                    &          &          &            &          & $(0.06)$     \\
\hline
R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
\hline
\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{HealthRegressions-DietaryKnowledge}
\end{center}
\end{table}

\begin{table}
\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
\begin{center}
\scalebox{0.8}{
\begin{tabular}{l c c c c c }
\hline
 & (1) & (2) & (3) & (4) & (5) \\
\hline
(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
ML1                 &              &          &              &            & $0.03$       \\
                    &              &          &              &            & $(0.07)$     \\
ML2                 &              &          &              &            & $0.47^{***}$ \\
                    &              &          &              &            & $(0.05)$     \\
ML3                 &              &          &              &            & $0.24^{***}$ \\
                    &              &          &              &            & $(0.05)$     \\
\hline
R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
\hline
\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
\end{tabular}
}
\label{HealthRegressions-AppreciateHealthy}
\end{center}
\end{table}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:21 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
  \label{lessIllOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
  \label{dietaryOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
  \label{appreciateOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Thu, Feb 27, 2020 - 10:27:23 PM
% Requires LaTeX packages: dcolumn 
\begin{table}[!htbp] \centering 
  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
  \label{selfworthOdds} 
\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
\hline \\[-1.8ex] 
\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}
